Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-10 paper.qmd
Updated Figure 12

XXX can we use a and e in these figures instead of a and b, so it is easier to describe relative to the first figure, and previous figure?

@@

trimesh_removed_pbmc_best <- ggplot() + 
  geom_point(
    data = tsne_pbmc_scaled_best_with_cluster,
    aes(
      x = tSNE1,
      y = tSNE2,
      color = cluster
    ),
    alpha = 0.3#,
    #color = "#999999"
  ) +
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("b1", cex = 2, c(0.08, 0.9)) +
  theme(
    aspect.ratio = 1
  )
```

@@

pbmc_proj_tsne_model1_best <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "b2", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model2_best <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1, 0.75), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "b3", cex = 2) + 
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))
```

>>>>

<!-- XXX can we use a and e in these figures instead of a and b, so it is easier to describe relative to the first figure, and previous figure? -->

@@

trimesh_removed_pbmc_best <- ggplot() + 
  geom_point(
    data = tsne_pbmc_scaled_best_with_cluster,
    aes(
      x = tSNE1,
      y = tSNE2,
      color = cluster
    ),
    alpha = 0.3#,
    #color = "#999999"
  ) +
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("e1", cex = 2, c(0.08, 0.9)) +
  theme(
    aspect.ratio = 1
  )
```

@@

pbmc_proj_tsne_model1_best <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "e2", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model2_best <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1, 0.75), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "e3", cex = 2) + 
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))
```
